Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-06-13 response to reviewer.tex

\newcommand{\filt}[6]{
\[
\begin{xy}
\xymatrix@R20pt@C20pt{
&\mathbb{C}^3&\\\langle #1,#2 \rangle\ar[ru]&\langle #3,#4\rangle\ar[u]&\langle #5,#6\rangle\ar[lu]\\\langle #1\rangle\ar[u]&\langle #3\rangle\ar[u]&\langle #5\rangle\ar[u]}
\end{xy}
\]
} 
\begin{document}
\pagestyle{empty}

\noindent{\bf Response to the reviewer - Cell decompositions for rank two quiver Grassmannians}\\

\noindent In the following, we point out the changes made and give responses to the referee's comments..

\renewcommand{\labelenumi}{(\arabic{enumi})}
\begin{enumerate}
  \item[Section 3.1] The referee's suggestions were incorporated into a shortened proof of Lemmas 3.4 and motivated a rewriting of the proof of Lemma 3.9.
    We could not see how to use irreducibility to prove Lemma 3.15, it is not clear why a subrepresentation $U \subset \tilde P_{m+1}^V$ lifts to a map $U \to \tilde P_{m+1}$ rather than giving rise to a map $\tilde P_{m+1} \to U$.
  \item[Lemma 3.30] The referee's comments offer a pleasing non-inductive viewpoint towards evaluating this kernel and thus have been incorporated into a new clarified proof.
  \item[Corollary 3.32] The notation of perpendicular categories has been incorporated into the statement of the result.
  \item[Definition 3.33] We had overlooked this simple viewpoint on admissible sequences and thank the referee for these extremely helpful remarks.
    The entire section has been somewhat reorganized to better capture the nature of the construction.
  \item[After Definition 3.33] After the reorganization, this notation is no longer being used.
  \item[Before Lemma 3.34] This typo has been corrected.
  \item[Lemma 3.34] Lemma 3.34 (now 3.33) has been rewritten to clarify the inductive structure of truncated preprojectives following the change of focus onto admissible sequences.
  \item[Section 4.2] This is a matter of convention.
    In general, the placement of the $*$'s for an attracting set is equivalent to the choice of the map $d:\{1,\ldots,n\}\to\ZZ$, cells of our chosen form impose the condition $d(1)>\cdots>d(n)$.
  \item[Lemma 4.3] We have added references to Cerulli Irelli and Haupt at the beginning of Section 4.2.
    However, Haupt's statement is stronger than his proof since it assumes a thin lift to an abelian cover, a trait our representations rarely possess.
    Furthermore, it does not seem to be straightforward to obtain our explicit description of the fixed point set of the quiver Grassmannians as those subrepresentations which live on the universal abelian covering with Haupt's result. 
  \item[Section 4.4] The dependence of various Caldero-Chapoton maps on their defining sequences has been clarified.
  \item[Theorem 4.20] 
\end{enumerate}

### 2019-06-13 Grassmannian_cells.tex
Restored the old proof of Lemma 3.15

\begin{lemma}
  \label{le:projective subrepresentations}
  For $V\in \Gr(\cH_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
\end{lemma}
\begin{proof}
  Since the map $ev_V$ in equation \eqref{eq:truncated preprojectives} is irreducible, every proper subrepresentation of $P_{m+1}^V$ factors through $P_{m+1}$ and the claim follows from Lemma~\ref{le:preprojective subs}.
\qed\end{proof}
% We proceed by induction on $m$.
% When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
% In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.

>>>>

\begin{lemma}
  \label{le:projective subrepresentations}
  For $V\in \Gr(\cH_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
\end{lemma}
\begin{proof}
  We proceed by induction on $m$.
  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.

  For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
  Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
\qed\end{proof}
% We proceed by induction on $m$.
% When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
% In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.
